Pass 3 Comparison

### 2025-04-09 studies/pass3_comparison.qmd
remove excluded studies from bib template
rendered the html versions

```{r}
bib_df_merged$NOTES_INDEX.CA <- NULL
bib_df_merged$NOTES_INDEX.TE <- NULL
bib_df_merged$CATEGORY <- NULL
```

@@

Notes:

For Feature classification, use this one:

https://ieeexplore.ieee.org/stamp/stamp.jsp?arnumber=9229494

Insert the template the annotation fields from googledoc to the bibtex file.

>>>>

```{r}
bib_df_merged$NOTES_INDEX.CA <- NULL
bib_df_merged$NOTES_INDEX.TE <- NULL
```

@@
